---
title: "R Notebook"
output: html_notebook
---

```{r}
source("FunctionJuan.R")
```

```{r, include=FALSE}
library(tidyverse)

df <- read.csv("rawdata.csv")

multiples_regresiones(df, 1:22, 23:34) %>%
  select(fondo, term, 2:14) %>%
  xtable() %>%
  print(type = "html")
```

<table border=1>
<tr> <th>  </th> <th> fondo </th> <th> term </th> <th> (Intercept) </th> <th> Asian.Index.in.GBP </th> <th> Europe.Dividend.Index.in.GBP </th> <th> Europe.Index.in.GBP </th> <th> FTSE.ASX.Index.in.GBP </th> <th> FTSE.Dividend.Index.in.GBP </th> <th> FTSE.Small.Cap.Index.in.GBP </th> <th> Japan.Index.in.GBP </th> <th> Japan.Index.Smaller.Companies.in.GBP </th> <th> SPXTR.Dividend.Index.in.GBP </th> <th> SPXTR.Index.in.GBP </th> <th> World.Emerging.Markets.in.GBP </th> <th> World.Index.in.GBP </th>  </tr>
  <tr> <td align="right"> 1 </td> <td> Asian.Fund.....Sterling.R.Acc </td> <td> Beta </td> <td align="right"> -0.00 </td> <td align="right"> 0.74 </td> <td align="right"> -0.04 </td> <td align="right"> -0.04 </td> <td align="right"> -0.03 </td> <td align="right"> 0.04 </td> <td align="right"> 0.07 </td> <td align="right"> 0.11 </td> <td align="right"> -0.07 </td> <td align="right"> -0.04 </td> <td align="right"> 0.07 </td> <td align="right"> 0.16 </td> <td align="right"> -0.01 </td> </tr>
  <tr> <td align="right"> 2 </td> <td> Asian.Fund.....Sterling.R.Acc </td> <td> t-statistic </td> <td align="right"> -1.04 </td> <td align="right"> 12.57 </td> <td align="right"> -0.67 </td> <td align="right"> -0.89 </td> <td align="right"> -0.50 </td> <td align="right"> 0.90 </td> <td align="right"> 1.61 </td> <td align="right"> 2.56 </td> <td align="right"> -1.67 </td> <td align="right"> -0.82 </td> <td align="right"> 0.78 </td> <td align="right"> 2.85 </td> <td align="right"> -0.11 </td> </tr>
  <tr> <td align="right"> 3 </td> <td> Dividend.Fund.....Sterling.R.Acc </td> <td> Beta </td> <td align="right"> -0.00 </td> <td align="right"> 0.17 </td> <td align="right"> 0.03 </td> <td align="right"> -0.01 </td> <td align="right"> 0.69 </td> <td align="right"> 0.02 </td> <td align="right"> 0.16 </td> <td align="right"> -0.08 </td> <td align="right"> 0.07 </td> <td align="right"> -0.07 </td> <td align="right"> 0.08 </td> <td align="right"> -0.11 </td> <td align="right"> -0.02 </td> </tr>
  <tr> <td align="right"> 4 </td> <td> Dividend.Fund.....Sterling.R.Acc </td> <td> t-statistic </td> <td align="right"> -1.51 </td> <td align="right"> 3.17 </td> <td align="right"> 0.46 </td> <td align="right"> -0.31 </td> <td align="right"> 11.39 </td> <td align="right"> 0.42 </td> <td align="right"> 3.95 </td> <td align="right"> -2.06 </td> <td align="right"> 2.03 </td> <td align="right"> -1.63 </td> <td align="right"> 1.09 </td> <td align="right"> -2.28 </td> <td align="right"> -0.19 </td> </tr>
  <tr> <td align="right"> 5 </td> <td> European.Index.Tracker.Fund.....Sterling.A.Acc </td> <td> Beta </td> <td align="right"> -0.00 </td> <td align="right"> 0.41 </td> <td align="right"> 0.02 </td> <td align="right"> 0.81 </td> <td align="right"> -0.03 </td> <td align="right"> -0.06 </td> <td align="right"> 0.17 </td> <td align="right"> 0.22 </td> <td align="right"> -0.10 </td> <td align="right"> -0.00 </td> <td align="right"> -0.24 </td> <td align="right"> -0.20 </td> <td align="right"> 0.04 </td> </tr>
  <tr> <td align="right"> 6 </td> <td> European.Index.Tracker.Fund.....Sterling.A.Acc </td> <td> t-statistic </td> <td align="right"> -1.23 </td> <td align="right"> 6.72 </td> <td align="right"> 0.29 </td> <td align="right"> 16.00 </td> <td align="right"> -0.43 </td> <td align="right"> -1.15 </td> <td align="right"> 3.67 </td> <td align="right"> 4.76 </td> <td align="right"> -2.32 </td> <td align="right"> -0.07 </td> <td align="right"> -2.70 </td> <td align="right"> -3.46 </td> <td align="right"> 0.32 </td> </tr>
  <tr> <td align="right"> 7 </td> <td> European.Select.Fund.....Sterling.R.Acc </td> <td> Beta </td> <td align="right"> -0.00 </td> <td align="right"> 0.05 </td> <td align="right"> 0.02 </td> <td align="right"> 0.68 </td> <td align="right"> -0.03 </td> <td align="right"> -0.05 </td> <td align="right"> 0.16 </td> <td align="right"> 0.08 </td> <td align="right"> -0.05 </td> <td align="right"> -0.08 </td> <td align="right"> 0.02 </td> <td align="right"> -0.04 </td> <td align="right"> 0.16 </td> </tr>
  <tr> <td align="right"> 8 </td> <td> European.Select.Fund.....Sterling.R.Acc </td> <td> t-statistic </td> <td align="right"> -1.00 </td> <td align="right"> 0.86 </td> <td align="right"> 0.30 </td> <td align="right"> 13.43 </td> <td align="right"> -0.41 </td> <td align="right"> -0.97 </td> <td align="right"> 3.49 </td> <td align="right"> 1.75 </td> <td align="right"> -1.25 </td> <td align="right"> -1.64 </td> <td align="right"> 0.21 </td> <td align="right"> -0.63 </td> <td align="right"> 1.17 </td> </tr>
  <tr> <td align="right"> 9 </td> <td> European.Smaller.Companies.Fund.....Sterling.R.Acc </td> <td> Beta </td> <td align="right"> 0.00 </td> <td align="right"> 0.14 </td> <td align="right"> -0.06 </td> <td align="right"> 0.59 </td> <td align="right"> 0.02 </td> <td align="right"> -0.08 </td> <td align="right"> 0.51 </td> <td align="right"> -0.09 </td> <td align="right"> 0.03 </td> <td align="right"> -0.18 </td> <td align="right"> -0.08 </td> <td align="right"> -0.03 </td> <td align="right"> 0.23 </td> </tr>
  <tr> <td align="right"> 10 </td> <td> European.Smaller.Companies.Fund.....Sterling.R.Acc </td> <td> t-statistic </td> <td align="right"> 0.82 </td> <td align="right"> 1.62 </td> <td align="right"> -0.65 </td> <td align="right"> 8.20 </td> <td align="right"> 0.17 </td> <td align="right"> -1.14 </td> <td align="right"> 7.73 </td> <td align="right"> -1.38 </td> <td align="right"> 0.45 </td> <td align="right"> -2.61 </td> <td align="right"> -0.66 </td> <td align="right"> -0.42 </td> <td align="right"> 1.20 </td> </tr>
  <tr> <td align="right"> 11 </td> <td> European.Strategic.Value.Fund.....Sterling.R.Acc </td> <td> Beta </td> <td align="right"> -0.00 </td> <td align="right"> 0.10 </td> <td align="right"> -0.08 </td> <td align="right"> 0.57 </td> <td align="right"> 0.14 </td> <td align="right"> 0.12 </td> <td align="right"> 0.07 </td> <td align="right"> 0.11 </td> <td align="right"> -0.06 </td> <td align="right"> -0.05 </td> <td align="right"> 0.07 </td> <td align="right"> -0.03 </td> <td align="right"> -0.09 </td> </tr>
  <tr> <td align="right"> 12 </td> <td> European.Strategic.Value.Fund.....Sterling.R.Acc </td> <td> t-statistic </td> <td align="right"> -1.18 </td> <td align="right"> 1.72 </td> <td align="right"> -1.32 </td> <td align="right"> 12.01 </td> <td align="right"> 2.23 </td> <td align="right"> 2.63 </td> <td align="right"> 1.55 </td> <td align="right"> 2.52 </td> <td align="right"> -1.43 </td> <td align="right"> -1.06 </td> <td align="right"> 0.88 </td> <td align="right"> -0.56 </td> <td align="right"> -0.71 </td> </tr>
  <tr> <td align="right"> 13 </td> <td> Global.Basics.Fund.....Sterling.R.Acc </td> <td> Beta </td> <td align="right"> -0.00 </td> <td align="right"> 0.44 </td> <td align="right"> 0.11 </td> <td align="right"> -0.03 </td> <td align="right"> 0.09 </td> <td align="right"> -0.10 </td> <td align="right"> 0.24 </td> <td align="right"> 0.08 </td> <td align="right"> -0.02 </td> <td align="right"> -0.13 </td> <td align="right"> -0.21 </td> <td align="right"> -0.10 </td> <td align="right"> 0.64 </td> </tr>
  <tr> <td align="right"> 14 </td> <td> Global.Basics.Fund.....Sterling.R.Acc </td> <td> t-statistic </td> <td align="right"> -2.07 </td> <td align="right"> 5.94 </td> <td align="right"> 1.31 </td> <td align="right"> -0.50 </td> <td align="right"> 1.11 </td> <td align="right"> -1.55 </td> <td align="right"> 4.25 </td> <td align="right"> 1.39 </td> <td align="right"> -0.48 </td> <td align="right"> -2.25 </td> <td align="right"> -1.92 </td> <td align="right"> -1.35 </td> <td align="right"> 3.88 </td> </tr>
  <tr> <td align="right"> 15 </td> <td> Global.Dividend.Fund.....Sterling.R.Acc </td> <td> Beta </td> <td align="right"> -0.00 </td> <td align="right"> 0.26 </td> <td align="right"> 0.09 </td> <td align="right"> 0.05 </td> <td align="right"> 0.07 </td> <td align="right"> -0.01 </td> <td align="right"> 0.11 </td> <td align="right"> 0.04 </td> <td align="right"> 0.02 </td> <td align="right"> 0.06 </td> <td align="right"> 0.04 </td> <td align="right"> -0.12 </td> <td align="right"> 0.35 </td> </tr>
  <tr> <td align="right"> 16 </td> <td> Global.Dividend.Fund.....Sterling.R.Acc </td> <td> t-statistic </td> <td align="right"> -1.57 </td> <td align="right"> 3.94 </td> <td align="right"> 1.29 </td> <td align="right"> 0.89 </td> <td align="right"> 0.91 </td> <td align="right"> -0.17 </td> <td align="right"> 2.12 </td> <td align="right"> 0.87 </td> <td align="right"> 0.51 </td> <td align="right"> 1.20 </td> <td align="right"> 0.46 </td> <td align="right"> -1.91 </td> <td align="right"> 2.41 </td> </tr>
  <tr> <td align="right"> 17 </td> <td> Global.Emerging.Markets.Fund.....Sterling.R.Acc </td> <td> Beta </td> <td align="right"> -0.00 </td> <td align="right"> 0.14 </td> <td align="right"> 0.02 </td> <td align="right"> -0.03 </td> <td align="right"> -0.05 </td> <td align="right"> 0.05 </td> <td align="right"> 0.03 </td> <td align="right"> 0.09 </td> <td align="right"> -0.07 </td> <td align="right"> -0.02 </td> <td align="right"> -0.07 </td> <td align="right"> 0.80 </td> <td align="right"> 0.01 </td> </tr>
  <tr> <td align="right"> 18 </td> <td> Global.Emerging.Markets.Fund.....Sterling.R.Acc </td> <td> t-statistic </td> <td align="right"> -0.27 </td> <td align="right"> 2.37 </td> <td align="right"> 0.25 </td> <td align="right"> -0.65 </td> <td align="right"> -0.65 </td> <td align="right"> 0.95 </td> <td align="right"> 0.72 </td> <td align="right"> 1.93 </td> <td align="right"> -1.55 </td> <td align="right"> -0.34 </td> <td align="right"> -0.83 </td> <td align="right"> 13.83 </td> <td align="right"> 0.09 </td> </tr>
  <tr> <td align="right"> 19 </td> <td> Global.Leaders.Fund.....Sterling.R.Acc </td> <td> Beta </td> <td align="right"> -0.00 </td> <td align="right"> 0.20 </td> <td align="right"> 0.01 </td> <td align="right"> 0.10 </td> <td align="right"> 0.01 </td> <td align="right"> 0.02 </td> <td align="right"> 0.11 </td> <td align="right"> 0.10 </td> <td align="right"> 0.04 </td> <td align="right"> -0.03 </td> <td align="right"> 0.19 </td> <td align="right"> -0.09 </td> <td align="right"> 0.34 </td> </tr>
  <tr> <td align="right"> 20 </td> <td> Global.Leaders.Fund.....Sterling.R.Acc </td> <td> t-statistic </td> <td align="right"> -1.78 </td> <td align="right"> 3.20 </td> <td align="right"> 0.11 </td> <td align="right"> 1.88 </td> <td align="right"> 0.12 </td> <td align="right"> 0.45 </td> <td align="right"> 2.21 </td> <td align="right"> 2.15 </td> <td align="right"> 1.01 </td> <td align="right"> -0.51 </td> <td align="right"> 2.05 </td> <td align="right"> -1.52 </td> <td align="right"> 2.36 </td> </tr>
  <tr> <td align="right"> 21 </td> <td> Global.Recovery.Fund.....Sterling.R.Acc </td> <td> Beta </td> <td align="right"> -0.00 </td> <td align="right"> 0.16 </td> <td align="right"> -0.04 </td> <td align="right"> 0.06 </td> <td align="right"> -0.04 </td> <td align="right"> 0.05 </td> <td align="right"> 0.09 </td> <td align="right"> 0.02 </td> <td align="right"> 0.03 </td> <td align="right"> -0.09 </td> <td align="right"> 0.14 </td> <td align="right"> -0.10 </td> <td align="right"> 0.62 </td> </tr>
  <tr> <td align="right"> 22 </td> <td> Global.Recovery.Fund.....Sterling.R.Acc </td> <td> t-statistic </td> <td align="right"> -1.60 </td> <td align="right"> 2.32 </td> <td align="right"> -0.56 </td> <td align="right"> 1.04 </td> <td align="right"> -0.47 </td> <td align="right"> 0.84 </td> <td align="right"> 1.62 </td> <td align="right"> 0.30 </td> <td align="right"> 0.69 </td> <td align="right"> -1.63 </td> <td align="right"> 1.41 </td> <td align="right"> -1.49 </td> <td align="right"> 3.99 </td> </tr>
  <tr> <td align="right"> 23 </td> <td> Global.Select.Fund.....Sterling.R.Acc </td> <td> Beta </td> <td align="right"> -0.00 </td> <td align="right"> 0.16 </td> <td align="right"> -0.02 </td> <td align="right"> 0.18 </td> <td align="right"> 0.06 </td> <td align="right"> -0.05 </td> <td align="right"> 0.09 </td> <td align="right"> 0.09 </td> <td align="right"> -0.01 </td> <td align="right"> 0.02 </td> <td align="right"> 0.09 </td> <td align="right"> -0.07 </td> <td align="right"> 0.39 </td> </tr>
  <tr> <td align="right"> 24 </td> <td> Global.Select.Fund.....Sterling.R.Acc </td> <td> t-statistic </td> <td align="right"> -1.23 </td> <td align="right"> 2.67 </td> <td align="right"> -0.23 </td> <td align="right"> 3.59 </td> <td align="right"> 0.91 </td> <td align="right"> -1.03 </td> <td align="right"> 2.00 </td> <td align="right"> 1.87 </td> <td align="right"> -0.21 </td> <td align="right"> 0.40 </td> <td align="right"> 1.05 </td> <td align="right"> -1.22 </td> <td align="right"> 2.88 </td> </tr>
  <tr> <td align="right"> 25 </td> <td> Index.Tracker.Fund.....Sterling.A.Acc </td> <td> Beta </td> <td align="right"> -0.00 </td> <td align="right"> 0.42 </td> <td align="right"> 0.12 </td> <td align="right"> -0.08 </td> <td align="right"> 0.67 </td> <td align="right"> 0.07 </td> <td align="right"> 0.05 </td> <td align="right"> 0.11 </td> <td align="right"> -0.09 </td> <td align="right"> -0.00 </td> <td align="right"> -0.26 </td> <td align="right"> -0.22 </td> <td align="right"> 0.17 </td> </tr>
  <tr> <td align="right"> 26 </td> <td> Index.Tracker.Fund.....Sterling.A.Acc </td> <td> t-statistic </td> <td align="right"> -0.27 </td> <td align="right"> 7.40 </td> <td align="right"> 1.89 </td> <td align="right"> -1.68 </td> <td align="right"> 10.36 </td> <td align="right"> 1.55 </td> <td align="right"> 1.26 </td> <td align="right"> 2.60 </td> <td align="right"> -2.19 </td> <td align="right"> -0.07 </td> <td align="right"> -3.20 </td> <td align="right"> -4.06 </td> <td align="right"> 1.33 </td> </tr>
  <tr> <td align="right"> 27 </td> <td> Japan.Fund.....Sterling.R.Acc </td> <td> Beta </td> <td align="right"> -0.00 </td> <td align="right"> -0.06 </td> <td align="right"> 0.02 </td> <td align="right"> -0.14 </td> <td align="right"> -0.05 </td> <td align="right"> 0.19 </td> <td align="right"> 0.15 </td> <td align="right"> 0.79 </td> <td align="right"> -0.02 </td> <td align="right"> -0.14 </td> <td align="right"> 0.28 </td> <td align="right"> 0.13 </td> <td align="right"> -0.17 </td> </tr>
  <tr> <td align="right"> 28 </td> <td> Japan.Fund.....Sterling.R.Acc </td> <td> t-statistic </td> <td align="right"> -0.87 </td> <td align="right"> -0.74 </td> <td align="right"> 0.18 </td> <td align="right"> -1.99 </td> <td align="right"> -0.57 </td> <td align="right"> 2.78 </td> <td align="right"> 2.31 </td> <td align="right"> 12.63 </td> <td align="right"> -0.38 </td> <td align="right"> -2.13 </td> <td align="right"> 2.36 </td> <td align="right"> 1.62 </td> <td align="right"> -0.93 </td> </tr>
  <tr> <td align="right"> 29 </td> <td> Japan.Smaller.Companies.Fund.....Sterling.R.Acc </td> <td> Beta </td> <td align="right"> 0.00 </td> <td align="right"> -0.22 </td> <td align="right"> 0.07 </td> <td align="right"> -0.02 </td> <td align="right"> -0.02 </td> <td align="right"> -0.02 </td> <td align="right"> 0.14 </td> <td align="right"> 0.16 </td> <td align="right"> 0.76 </td> <td align="right"> -0.12 </td> <td align="right"> 0.23 </td> <td align="right"> 0.05 </td> <td align="right"> -0.04 </td> </tr>
  <tr> <td align="right"> 30 </td> <td> Japan.Smaller.Companies.Fund.....Sterling.R.Acc </td> <td> t-statistic </td> <td align="right"> 1.37 </td> <td align="right"> -2.68 </td> <td align="right"> 0.79 </td> <td align="right"> -0.36 </td> <td align="right"> -0.17 </td> <td align="right"> -0.37 </td> <td align="right"> 2.23 </td> <td align="right"> 2.63 </td> <td align="right"> 13.30 </td> <td align="right"> -1.81 </td> <td align="right"> 1.96 </td> <td align="right"> 0.64 </td> <td align="right"> -0.21 </td> </tr>
  <tr> <td align="right"> 31 </td> <td> North.American.Dividend.Fund.....Sterling.R.Acc </td> <td> Beta </td> <td align="right"> -0.00 </td> <td align="right"> 0.10 </td> <td align="right"> 0.07 </td> <td align="right"> -0.07 </td> <td align="right"> 0.00 </td> <td align="right"> -0.09 </td> <td align="right"> 0.18 </td> <td align="right"> 0.00 </td> <td align="right"> 0.01 </td> <td align="right"> 0.09 </td> <td align="right"> 0.40 </td> <td align="right"> -0.12 </td> <td align="right"> 0.40 </td> </tr>
  <tr> <td align="right"> 32 </td> <td> North.American.Dividend.Fund.....Sterling.R.Acc </td> <td> t-statistic </td> <td align="right"> -1.60 </td> <td align="right"> 1.22 </td> <td align="right"> 0.78 </td> <td align="right"> -1.04 </td> <td align="right"> 0.05 </td> <td align="right"> -1.36 </td> <td align="right"> 2.87 </td> <td align="right"> 0.02 </td> <td align="right"> 0.25 </td> <td align="right"> 1.39 </td> <td align="right"> 3.37 </td> <td align="right"> -1.56 </td> <td align="right"> 2.21 </td> </tr>
  <tr> <td align="right"> 33 </td> <td> North.American.Value.Fund.....Sterling.R.Acc </td> <td> Beta </td> <td align="right"> -0.00 </td> <td align="right"> 0.85 </td> <td align="right"> 0.15 </td> <td align="right"> -0.17 </td> <td align="right"> -0.03 </td> <td align="right"> -0.14 </td> <td align="right"> 0.35 </td> <td align="right"> 0.49 </td> <td align="right"> -0.21 </td> <td align="right"> -0.02 </td> <td align="right"> 0.19 </td> <td align="right"> -0.62 </td> <td align="right"> 0.33 </td> </tr>
  <tr> <td align="right"> 34 </td> <td> North.American.Value.Fund.....Sterling.R.Acc </td> <td> t-statistic </td> <td align="right"> -1.02 </td> <td align="right"> 6.84 </td> <td align="right"> 1.08 </td> <td align="right"> -1.62 </td> <td align="right"> -0.21 </td> <td align="right"> -1.32 </td> <td align="right"> 3.69 </td> <td align="right"> 5.27 </td> <td align="right"> -2.43 </td> <td align="right"> -0.24 </td> <td align="right"> 1.07 </td> <td align="right"> -5.27 </td> <td align="right"> 1.21 </td> </tr>
  <tr> <td align="right"> 35 </td> <td> Pan.European.Dividend.Fund.....Sterling.R.Acc </td> <td> Beta </td> <td align="right"> -0.00 </td> <td align="right"> 0.40 </td> <td align="right"> 0.17 </td> <td align="right"> 0.39 </td> <td align="right"> 0.19 </td> <td align="right"> -0.02 </td> <td align="right"> 0.04 </td> <td align="right"> 0.13 </td> <td align="right"> -0.07 </td> <td align="right"> 0.06 </td> <td align="right"> -0.26 </td> <td align="right"> -0.27 </td> <td align="right"> 0.15 </td> </tr>
  <tr> <td align="right"> 36 </td> <td> Pan.European.Dividend.Fund.....Sterling.R.Acc </td> <td> t-statistic </td> <td align="right"> -0.31 </td> <td align="right"> 6.65 </td> <td align="right"> 2.58 </td> <td align="right"> 7.81 </td> <td align="right"> 2.72 </td> <td align="right"> -0.40 </td> <td align="right"> 0.80 </td> <td align="right"> 2.90 </td> <td align="right"> -1.57 </td> <td align="right"> 1.23 </td> <td align="right"> -2.95 </td> <td align="right"> -4.78 </td> <td align="right"> 1.15 </td> </tr>
  <tr> <td align="right"> 37 </td> <td> Pan.European.Select.Fund.....Sterling.R.Acc </td> <td> Beta </td> <td align="right"> -0.00 </td> <td align="right"> 0.07 </td> <td align="right"> -0.01 </td> <td align="right"> 0.50 </td> <td align="right"> 0.22 </td> <td align="right"> 0.01 </td> <td align="right"> 0.08 </td> <td align="right"> 0.01 </td> <td align="right"> -0.01 </td> <td align="right"> -0.05 </td> <td align="right"> -0.04 </td> <td align="right"> 0.03 </td> <td align="right"> 0.08 </td> </tr>
  <tr> <td align="right"> 38 </td> <td> Pan.European.Select.Fund.....Sterling.R.Acc </td> <td> t-statistic </td> <td align="right"> -1.55 </td> <td align="right"> 1.17 </td> <td align="right"> -0.22 </td> <td align="right"> 10.50 </td> <td align="right"> 3.31 </td> <td align="right"> 0.26 </td> <td align="right"> 1.84 </td> <td align="right"> 0.30 </td> <td align="right"> -0.18 </td> <td align="right"> -1.03 </td> <td align="right"> -0.47 </td> <td align="right"> 0.47 </td> <td align="right"> 0.64 </td> </tr>
  <tr> <td align="right"> 39 </td> <td> Recovery.Fund.....Sterling.R.Acc </td> <td> Beta </td> <td align="right"> -0.00 </td> <td align="right"> 0.11 </td> <td align="right"> -0.09 </td> <td align="right"> -0.02 </td> <td align="right"> 0.80 </td> <td align="right"> -0.06 </td> <td align="right"> 0.26 </td> <td align="right"> -0.01 </td> <td align="right"> 0.00 </td> <td align="right"> -0.03 </td> <td align="right"> 0.11 </td> <td align="right"> -0.08 </td> <td align="right"> -0.01 </td> </tr>
  <tr> <td align="right"> 40 </td> <td> Recovery.Fund.....Sterling.R.Acc </td> <td> t-statistic </td> <td align="right"> -2.08 </td> <td align="right"> 1.74 </td> <td align="right"> -1.27 </td> <td align="right"> -0.29 </td> <td align="right"> 10.85 </td> <td align="right"> -1.21 </td> <td align="right"> 5.21 </td> <td align="right"> -0.20 </td> <td align="right"> 0.07 </td> <td align="right"> -0.51 </td> <td align="right"> 1.16 </td> <td align="right"> -1.32 </td> <td align="right"> -0.07 </td> </tr>
  <tr> <td align="right"> 41 </td> <td> Smaller.Companies.Fund.....Sterling.R.Acc </td> <td> Beta </td> <td align="right"> 0.00 </td> <td align="right"> 0.23 </td> <td align="right"> -0.11 </td> <td align="right"> -0.09 </td> <td align="right"> 0.05 </td> <td align="right"> 0.19 </td> <td align="right"> 0.71 </td> <td align="right"> -0.02 </td> <td align="right"> -0.02 </td> <td align="right"> -0.21 </td> <td align="right"> -0.06 </td> <td align="right"> -0.20 </td> <td align="right"> 0.40 </td> </tr>
  <tr> <td align="right"> 42 </td> <td> Smaller.Companies.Fund.....Sterling.R.Acc </td> <td> t-statistic </td> <td align="right"> 0.80 </td> <td align="right"> 2.82 </td> <td align="right"> -1.22 </td> <td align="right"> -1.32 </td> <td align="right"> 0.57 </td> <td align="right"> 2.77 </td> <td align="right"> 11.21 </td> <td align="right"> -0.36 </td> <td align="right"> -0.27 </td> <td align="right"> -3.19 </td> <td align="right"> -0.51 </td> <td align="right"> -2.53 </td> <td align="right"> 2.17 </td> </tr>
  <tr> <td align="right"> 43 </td> <td> UK.Select.Fund.....Sterling.R.Acc </td> <td> Beta </td> <td align="right"> -0.00 </td> <td align="right"> 0.20 </td> <td align="right"> -0.11 </td> <td align="right"> 0.07 </td> <td align="right"> 0.81 </td> <td align="right"> 0.06 </td> <td align="right"> 0.17 </td> <td align="right"> 0.07 </td> <td align="right"> -0.03 </td> <td align="right"> -0.06 </td> <td align="right"> 0.16 </td> <td align="right"> -0.17 </td> <td align="right"> -0.19 </td> </tr>
  <tr> <td align="right"> 44 </td> <td> UK.Select.Fund.....Sterling.R.Acc </td> <td> t-statistic </td> <td align="right"> -1.55 </td> <td align="right"> 3.32 </td> <td align="right"> -1.71 </td> <td align="right"> 1.37 </td> <td align="right"> 11.79 </td> <td align="right"> 1.23 </td> <td align="right"> 3.69 </td> <td align="right"> 1.56 </td> <td align="right"> -0.74 </td> <td align="right"> -1.29 </td> <td align="right"> 1.82 </td> <td align="right"> -2.99 </td> <td align="right"> -1.40 </td> </tr>
   </table>
   

